### 2016-03-22 paper.tex
Add conservative conclusions section text

>>>>

Based on our design experiments, pilot study, and understanding of the
literature, we believe there is a significant potential for
culture-narration games as learning tools, particularly for
cultural empathy.
However, as with any educational intervention, these games do not
come without complications.

Physical games such as \totan{} and \smersh{} are expensive to produce
and, for many, intimidating to encounter. \totan{}'s \textbf{X}-page
instruction booklet may not faze a board game enthusiast, but we have
observed that others are intimidated by the large rulebook, heavy box,
and many components included in the game. Combined with the duration
of play and complexity of rules, such games seem inappropriate for use
in almost all formal educational settings such as conventional
schools.  However, we have found that the combination of technology
enhancement, grade-level writing, and shorter duration circumvents
these problems.  Digital implementations all but eliminate
distribution costs, and with clever game design, children can play the
game in the relatively chaotic environment of an informal after-school
program. With curriculum aides and improved scaffolding, such as
post-game debriefing, we are certain the game could be easily
integrated into school environments, particularly those with
ready access to computers.

The role of text within the game is worthy of particular attention.
The textual expression of narrative requires that players already possess
literacy skills: players who struggle with vocabulary or decoding words
are easily frustrated by such games. There is an opportunity
here as well, to differentiate text based on player reading level
or provide embedded reading aids; however, this also transforms
the outcome of the game from cultural empathy to reading literacy.
Player oration---having players read aloud to each
other---additionally requires oratory skills. We observed engagement
being enhanced when the reader employs theatrical talents as well.
The precise role of oratory skill, self-confidence, and the social
contract of gameplay (the ``magic circle'') is an area for future work.
